Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-10-18 reports/paper.tex
update zenodo doi
fix quote marks around solvophobic

\begin{abstract}
  In this work, we present the first example of the self-assembly of
  phospholipid monolayers at the interface between air and a non-aqueous
  liquid.
  Deep eutectic solvents are a novel class of environmentally friendly
  non-aqueous room temperature liquids with tunable properties, that have
  wide ranging potential applications and are capable of promoting the
  self-assembly of surfactant molecules.
  We use a chemically-consistent Bayesian modelling of X-ray and neutron
  reflectometry measurements to show that these monolayers broadly behave
  as they do on water.
  However, the ability of the deep eutectic solvent to interact with the
  phosphatidylglycerol lipid head, leads to an apparent increase in its
  volume compared to that observed in water.
  No such change was observed for the phosphocholine head, indicating that
  such interactions are head, and therefore solvent, specific.
  This has important implications for the potential uses of these solvents
  and for our understanding of how biomolecules behave in the absence of water.
\begin{description}
\item[Usage]
Electronic Supplementary Information (ESI) available: All analysis/plotting
scripts and figure files, allowing for a fully reproducible, and automated,
analysis workflow for the work presented is available at
\url{https://github.com/arm61/lipids_at_airdes} (DOI: **zenodo-doi**) under
a CC-BY 4.0 license.
Reduced experimental datasets are available at
\url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
\end{description}
\end{abstract}

@@

Deep eutectic solvents (DES) are green, sustainable liquids that are obtained
through the combination of ionic species with compounds that act as hydrogen
bond donors, such as sugars, alcohols, amines, and carboxylic
acids\cite{Smith2014,Dai2013}.
The resulting extensive hydrogen bonding network is able to stabilise the
ionic species and allows the eutectic mixture to remain liquid at room
temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
Through different combinations of the precursor materials, it is possible to
tune the solvent's physicochemical properties, such as
polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014},
network charge\cite{Zahn2016}, and
hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
Recently DES have also been shown to exhibit a "solvophobic" effect through
the promotion of surfactant micelle
formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018},
phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and
the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein
conformations\cite{Sanchez-Fernandez2017}.

>>>>

\begin{abstract}
  In this work, we present the first example of the self-assembly of
  phospholipid monolayers at the interface between air and a non-aqueous
  liquid.
  Deep eutectic solvents are a novel class of environmentally friendly
  non-aqueous room temperature liquids with tunable properties, that have
  wide ranging potential applications and are capable of promoting the
  self-assembly of surfactant molecules.
  We use a chemically-consistent Bayesian modelling of X-ray and neutron
  reflectometry measurements to show that these monolayers broadly behave
  as they do on water.
  However, the ability of the deep eutectic solvent to interact with the
  phosphatidylglycerol lipid head, leads to an apparent increase in its
  volume compared to that observed in water.
  No such change was observed for the phosphocholine head, indicating that
  such interactions are head, and therefore solvent, specific.
  This has important implications for the potential uses of these solvents
  and for our understanding of how biomolecules behave in the absence of water.
\begin{description}
\item[Usage]
Electronic Supplementary Information (ESI) available: All analysis/plotting
scripts and figure files, allowing for a fully reproducible, and automated,
analysis workflow for the work presented is available at
\url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.1464836)
under a CC-BY 4.0 license.
Reduced experimental datasets are available at
\url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
\end{description}
\end{abstract}

@@

Deep eutectic solvents (DES) are green, sustainable liquids that are obtained
through the combination of ionic species with compounds that act as hydrogen
bond donors, such as sugars, alcohols, amines, and carboxylic
acids\cite{Smith2014,Dai2013}.
The resulting extensive hydrogen bonding network is able to stabilise the
ionic species and allows the eutectic mixture to remain liquid at room
temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
Through different combinations of the precursor materials, it is possible to
tune the solvent's physicochemical properties, such as
polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014},
network charge\cite{Zahn2016}, and
hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
Recently DES have also been shown to exhibit a ``solvophobic'' effect through
the promotion of surfactant micelle
formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018},
phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and
the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein
conformations\cite{Sanchez-Fernandez2017}.
